opponent modelling

### 2019-11-11 comp_model_1019.Rmd
tried DEoptim

```{r}
# using some functions from the 'tidyverse' (also for me to get use to them ;-)
library(tidyr)
library(dplyr)
# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- as.numeric(cut(dat$round,2))
# create a new data.frame in a 'wide format'
# widedata <- dat %>%
#   unite(game_block,game,block) %>% # this creates a new variable which combines game and block
#     group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
#       summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
#         spread(game_block,mean_score) # reformat in the 'wide' format
# # save the data file as a .csv to use in e.g. SPSS
# write.csv(widedata,row.names=FALSE,file="scores_wide.csv")

@@

```{r}
# QL_modelling <- list()
# for(id in unique(dat$human_id)) {
#   QL_modelling[[id]] <- list()
#   tdat <- subset(dat,human_id == id)
#   QL_modelling[[id]] <- optim(c(0.1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.01), upper = c(0.99,10), method="L-BFGS-B")
# }
# 
# save(QL_modelling,file="QL_modelling.RData")
# 
# 
# ```
# 
# 
# ## Parametric EWA 
# 
# ```{r}
# 
# # Define reward matrices from the prospective of the row player (human in our case)
reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

@@

  lambda <- par[[1]]
  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper. 
  N <- 1.0

@@

EWA_self_modelling <- list()
for(id in unique(dat$human_id)) {
  EWA_self_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  EWA_self_modelling[[id]] <- optim(10.0,fn=EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.001, upper = 200, method="L-BFGS-B")
}

>>>>

```{r}
# using some functions from the 'tidyverse' (also for me to get use to them ;-)
library(tidyr)
library(dplyr)
library(DEoptim)
# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- as.numeric(cut(dat$round,2))
# create a new data.frame in a 'wide format'
# widedata <- dat %>%
#   unite(game_block,game,block) %>% # this creates a new variable which combines game and block
#     group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
#       summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
#         spread(game_block,mean_score) # reformat in the 'wide' format
# # save the data file as a .csv to use in e.g. SPSS
# write.csv(widedata,row.names=FALSE,file="scores_wide.csv")

@@

```{r}
# QL_modelling <- list()
# for(id in unique(dat$human_id)) {
#   QL_modelling[[id]] <- list()
#   tdat <- subset(dat,human_id == id)
#   QL_modelling[[id]] <- optim(c(0.1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.01), upper = c(0.99,10), method="L-BFGS-B")
# }
# 
# save(QL_modelling,file="QL_modelling.RData")
# 
#

```{r}
# 
# 
# ## Parametric EWA 
# 
# ```{r}
# 
# # Define reward matrices from the prospective of the row player (human in our case)
reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

@@

  lambda <- par[1]
  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper. 
  N <- 1.0

@@

EWA_self_modelling <- list()
for(id in unique(dat$human_id)) {
  EWA_self_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
#   EWA_self_modelling[[id]] <- optim(10.0,fn=EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
# }
  EWA_self_modelling[[id]] <- DEoptim(EWA_self, 0.0, 10.0, data=tdat,"-2loglik")
}
